MSDS_Project_Jeng

### 2016-12-02 MSDS_Project_Markdown.Rmd
Getting the score pull working

>>>>

url <- "http://www.gamerankings.com/browse.html?site=&cat=0&year=2016&numrev=1&sort=0&letter=&search="
SCORE_GET <- url %>% read_html() %>% html_nodes("table") %>% html_table(fill = TRUE)

# Rbind for appending

for (i in 1:9){
  url <- paste("http://www.gamerankings.com/browse.html?page=", i, "&year=2016&numrev=1", sep = "")
  SUBMETA_GET <- url %>% read_html %>% html_nodes("table") %>% html_table(fill = TRUE)

}
i = "1"
url <- "http://www.gamerankings.com/browse.html?page=1&year=2016&numrev=1"

paste("http://www.gamerankings.com/browse.html?page=", i, "&year=2016&numrev=1", sep = "")
